Phylogenetics and the human microbiome.

### 2014-04-05 reviews/response.txt

> 4) Pg. 14-15: I also don't really understand what UniFrac is or how it
> works, even after looking at Figure 2 (Olivier made a similar
> comment). Could we get some help here?

> 5) The figures need a bit of work. There seems to be some sort of
> equation at the bottom of Figure 1, but I can't decipher it. What do
> the colors mean in Figure 2? I don't find this to be very clear.

> 6) Pg. 20: "How to formulate a useful notion of independent contrasts
> (Felsenstein 1985) on such an object?" - Awkward wording.

I have changed this to "How might one formulate a useful notion of independent contrasts (Felsenstein 1985) on such an object?" I hope that's better.

@@

> My recommendation is acceptance pending minor to major changes.
> Actually, no change asked by the reviewers and me (see below) requires
> major efforts, but we all come from different origins, with different
> points of view and expectations, and thus summing all these demands
> will require a bit of time and attention. Basically, we all ask for
> more details and comments here and there, to make the paper more
> precise, comprehensive and self-contained. I am confident that you'll
> find our suggestions useful. I don't believe that the paper should be
> shortened in some places (or very locally), as suggested by Arne
> Mooers. When submitting your revision, please prepare a cover letter
> containing all the comments by the referees and me, with your
> changes/responses.

> Specific comments, possibly redundant with those from the reviewers,
> using Systematic Biology page numbering:

> P4	these techniques AND could

Thanks!

> P8	(Kuczynski et al. 2010). However, for more subtle information
> P8	"for more subtle information deeper sequencing is required" :
> what do you have in mind here?
> Indeed "distinguish between two rather different samples" is a modest
> goal Actually, it's not clear in this subsection what is meant by
> "Microbial community estimation" (title of the subsection). What is
> the goal here? Identify and classify microbes? Measure their
> abundance? Etc.? A few lines and explanations should suffice.

@@

> P24 Check "The presently used approach is rarefaction, which means
> uniform sub-sampling, typically without replacement to the number of
> reads in the lowest abundance sample"

> P25 Check "Comparative studies will continue to investigate what
> shapes and is shaped by the microbiome"

> P26 "during the 2013 LIRMM Mathematical and Computational Evolutionary
> Biology workshop", change LIRMM into MCEB

I have done so, so that the sentence reads "... 2013 MCEB Mathematical and Computational Evolutionary Biology workshop ..." is that right?

@@

> Reviewer 2, Arne Mooers
> -----------------------

> This was an interesting manuscript to read, and I compliment whoever
> thought to review Human Microbiome Research (HMR) for the SB
> readership. Overall, there is a lot of very interesting work reported
> on here, though I found the level of detail to be a bit uneven:
> sometimes we are told perhaps too much, and often, what feels like too
> little, in order to make the connections between HMR and SB. There is
> also seems to be some elision between HMR research and metagenomics
> more generally. That isn't a bad thing, but one does sometimes forget
> that we are focussed on HMR.

> Numbers refer to the SB manuscript pagination, rather than to the
> original latex.

> 4-45 additional to

> 5-8 delete and

Fixed.

> 7-23 delete though

Nice catch!

@@

> 7. On page 18, lines 26-27, RAxML is also implemented in QIIME.

> 8. On page 20, I think that this might be the place to discuss the
> potential use of phylogenetic networks in microbiome research (see
> Parks and Beiko 2012 Mol Biol Evol).

> 9. On page 24, when citing uBiome, it might also be fair to refer the
> similar crowd-funded American Gut Project.

> Typos:
> P3, L40: I would rather use "species delimitation" instead of "species definition".
> P4, L9: "These techniques and could be used"

Fixed.

> P6, L32: "we will be primarily be describing"

Whoops!

> P9, L29, L30: Maybe replace "diversity" by "variability"

Thanks.

> P18, L32: "a long history as a means to sequentially build"

> P19, L16: "GreenGenes 13_5 alignment has is almost 80% gaps"

Yikes, thanks.
